Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 Moltres.tex
Answer for reviewer question added

In case of strong scaling, the problem size keeps fixed but the number of processors is increased. 
The goal of strong scaling study is to find an optimal ratio between a number of processors and elements 
that allows the computation to finish in a reasonable amount of time, and does not waste too much computational
 power due to parallel overhead. We measured Moltres performance for the strong scaling of a simple 2D 
axisymmetric case for various problem sizes separately for intra-node (2,820; 5,640; 11,280 and 28,200 elements) 
and extra-node (86,655; 173,310; 317,735; 664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
CPU, 16 integer scheduling units, 32 virtual cores, nominal clock speed 2.3 GHz).

@@

For the weak scaling study, the part of the problem (workload) assigned to each processor stays constant and additional elements are 
used to solve a bigger problem which would not fit in memory on a single node. Thus, the weak scaling measurement is justification
 for memory-bound application such as multiphysics code. Linear weak scaling is achieved when the execution time stays constant 
 while the workload increasing in direct proportion to the number of cores. We performed Moltres weak-scaling tests on Blue Waters, 
 keeping the workload constant at 581, 985, 1970 and 3940 elements per core. \Cref{fig:intra_weak} shows Moltres weak scaling 
performance measured for 1 \ldots 32 core within one Blue Waters node and \Cref{fig:extra_weak} demonstrates performance for 
32 \ldots 128 core. As expected, the largest drop in performance occurs when the number of cores increases from one to $\approx$ 8, which 
corresponds to switching from no communication to a 2-D domain decomposition. The further reduction in performance of only about 50\% over 
a range of 32 cores is likely caused by increased communication latency appearing from collective MPI calls. For extra-node case, performance
 drops about three times most likely because of poor node selection by job scheduler and significantly increased latency and bandwidth costs.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.75\textwidth]{intra-node_weak.png}
  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of particles
per processor, for 1 \ldots 32 cores.}
  \label{fig:intra_weak}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.75\textwidth]{extra-node_weak.png}
  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of particles
per processor, for 32 \ldots 128 cores.}
  \label{fig:extra_weak}
\end{figure}

>>>>

In case of strong scaling, the problem size keeps fixed but the number of
processors is increased. The goal of strong scaling study is to find an
optimal ratio between a number of processors and elements that allows the
computation to finish in a reasonable amount of time, and does not waste
too much computational power due to parallel overhead. We measured
Moltres performance for the strong scaling of a simple 2D axisymmetric
case for various problem sizes separately for intra-node (2,820; 5,640;
11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
CPU, 16 integer scheduling units, 32 virtual units, nominal clock speed
2.3 GHz).

@@

For the weak scaling study, the part of the problem (workload) assigned
to each processor stays constant and additional elements are used to
solve a bigger problem which would not fit in memory on a single node.
Thus, the weak scaling measurement is justification for memory-bound
application such as multiphysics code. Linear weak scaling is achieved
when the execution time stays constant while the workload increasing
in direct proportion to the number of cores. We performed Moltres
weak-scaling tests on Blue Waters, keeping the workload constant at
581, 985, 1970 and 3940 elements per core. \Cref{fig:intra_weak} shows
Moltres weak scaling performance measured for 1 \ldots 32 core within
one Blue Waters node and \Cref{fig:extra_weak} demonstrates performance
for 32 \ldots 128 core. As expected, the largest drop in performance
occurs when the number of cores increases from one to $\approx$ 8, which 
corresponds to switching from no communication to a 2-D domain
decomposition. The further reduction in performance of only about 50\%
over a range of 32 cores is likely caused by increased communication
latency appearing from collective \gls{MPI} calls. For extra-node case,
performance drops about three times most likely because of poor node
selection by job scheduler and significantly increased latency and
bandwidth costs.

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.75\textwidth]{intra-node_weak.png}
  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
per processor, for 1 \ldots 32 cores.}
  \label{fig:intra_weak}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.75\textwidth]{extra-node_weak.png}
  \caption{Weak scaling performance of Moltres on Blue Waters, in seconds per element vs. number of processors, for a constant number of elements
per processor, for 32 \ldots 128 cores.}
  \label{fig:extra_weak}
\end{figure}
